A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-02-27 analysis/paper/paper_latex.Rmd
every implementation now has a reference, hurray

# Discussion
<!-- Some intro -->
Trajectory inference is unique among most other categories of single-cell analysis methods, such as clustering, normalisation and differential expression, because it models the data in a way that was almost impossible using bulk data. Indeed, for no other single-cell analysis types have so many tools been developed, according to omictools.org [@henry_omictoolsinformativedirectory_2014] (https://omictools.com/single-cell-rna-seq-category), the "awesome single cell software" list created by Sean Davis [@davis_awesomesinglecelllistsoftware_2018] and scRNA-tools [@zappia_exploringsinglecellrnaseq_2017] (https://www.scrna-tools.org) . It is therefore critical that these methods, now reaching `r sum(methods$is_ti, na.rm=TRUE)`, are evaluated to guide the users in their choice. In this preprint, we summarise the initial version of our evaluation of these methods, focusing on the quality control and the accuracy of their model using their default parameters on real and synthetic data.

>>>>

Performance was stable between real and synthetic datasets `r ref("sfig", "real_synthetic_comparison")`

```{r}
add_sfig(
        figure_file('real_synthetic_comparison.pdf', "5-optimise_parameters/5-real_synthetic_comparison")
, 
"real_synthetic_comparison", 
"Comparison of method performance between real and synthetic datasets. ", 
12, 
4
)
```
# Discussion
<!-- Some intro -->
Trajectory inference is unique among most other categories of single-cell analysis methods, such as clustering, normalisation and differential expression, because it models the data in a way that was almost impossible using bulk data. Indeed, for no other single-cell analysis types have so many tools been developed, according to omictools.org [@henry_omictoolsinformativedirectory_2014] (https://omictools.com/single-cell-rna-seq-category), the "awesome single cell software" list created by Sean Davis [@davis_awesomesinglecelllistsoftware_2018] and scRNA-tools [@zappia_exploringsinglecellrnaseq_2017] (https://www.scrna-tools.org) . It is therefore critical that these methods, now reaching `r sum(methods$is_ti, na.rm=TRUE)`, are evaluated to guide the users in their choice. In this preprint, we summarise the initial version of our evaluation of these methods, focusing on the quality control and the accuracy of their model using their default parameters on real and synthetic data.
